\documentclass[fyp]{socreport}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx} % to insert images
\usepackage{float}
%%% code block setups begin
\usepackage[newfloat]{minted}
\usepackage{xcolor} % to access the named colour LightGray
\definecolor{LightGray}{gray}{0.9}
\usepackage{caption}
\newenvironment{code}{\captionsetup{type=listing}}{}
\SetupFloatingEnvironment{listing}{name=Code}
%%% code block setups end
\usepackage{fullpage}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{amsmath}
\interfootnotelinepenalty=10000 %% Completely prevent breaking of footnotes
\usepackage{indentfirst}
%%% citation
\usepackage[backend = biber, style = apa]{biblatex}
\addbibresource{socreport.bib}
%%% footnote counter
\counterwithout{footnote}{chapter}
%%% reuse figure
\newcommand{\repeatcaption}[2]{%
  \renewcommand{\thefigure}{\ref{#1}}%
  \captionsetup{list=no}%
  \caption{#2 (repeated from page \pageref{#1})}%
  \addtocounter{figure}{-1}% So that next figure after the repeat gets the right number.
}

\begin{document}
\pagenumbering{roman}
\title{Competition Platform for AI Tasks}
\author{Tan Yuanhong}
\projyear{2021/22}
\projnumber{H247080}
\advisor{Dr. Akshay Narayan, Prof. Leong Tze Yun}
\deliverables{
	\item Report: 1 Volume
% 	\item Source Code: 6 Git Repository
}
\maketitle
\begin{abstract}
Entering the second decade of the 21st century, machine learning (ML) and artificial intelligence (AI) are the new must-haves for computer science education. Just like traditional algorithms, AI education requires evaluation of AI algorithms taught in class. However, while the data-oriented tasks like classification and regression have well-adopted platforms such as Kaggle, simulation-oriented tasks that are most common for reinforcement learning (RL) algorithms are yet to have a feature-complete online judging solution. This project aims to build a complete RL algorithm evaluation solution that is extensible, scalable, and easy-to-use. It covers four critical components of judging RL algorithms: a simulation environment framework, an auto-grading framework, a scalable and secure sandbox for arbitrary code execution, and finally a modern web application as the entry point. Besides comprehensive documentation and many quality-of-life new features, this project greatly improves the performance over existing internal platform (aiVLE 1.0) with a task queue system that not only distributes tasks fairly, but also dynamically adapts to the load of each worker node thanks to its resource awareness. Experimental results show that the new system provides equal task distribution among worker nodes and nearly three times of resource utilization improvement over aiVLE 1.0 ($\approx 85\%$ vs $\approx 30\%$).

\begin{project-nature}
	Implementation, Experimentation, Simulation
\end{project-nature}
\begin{keywords}
    \item Artificial Intelligence
	\item Machine Learning
\end{keywords}
\begin{implement}
	Ubuntu 20.04, Firejail 0.9.68, Python 3.8, Django 4.0, Celery 5.2
\end{implement}

\end{abstract}

\begin{acknowledgement}

Without the support of many people, this final year project would not have been possible. I would like to thank my advisors Dr. Narayan and Prof. Leong, who offered an unimaginable amount of guidance throughout this project with great kindness. Also thanks to School of Computing for their compute cluster nodes that made the experiments possible.\\

\noindent Finally, I would like to thank my friends and family for their support and love during the hard times of the COVID-19 pandemic. And special thanks my significant other for her patiently listening to my annoyingly frequent mentions of this project.

\end{acknowledgement}

\tableofcontents
\listoffigures 
\listoftables

\include{ch-introduction}
\include{ch-project_objective}
\include{ch-design_and_impl}
\include{ch-deployment_and_testing}
\include{ch-conclusion}

\renewcommand{\bibname}{References}
\setstretch{1}
\setlength\bibitemsep{1.75\itemsep}
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{References}
\printbibliography

\appendix
\include{appendix-list_of_links}
\include{appendix-aivle_gym}
\include{appendix-aivle_worker}
\include{appendix-aivle_web}
\include{appendix-deployment_issues}

\end{document}
